### 2017-07-26 sheets/talk-12/sheet-12.tex
Add example solutions for talk 12

@@

@@

@@

\pagebreak
\begin{exercise}
  Verify the correctness of the following graphical equations in braided monoidal categories by
  \begin{enumerate}
    \item the correctness theorem of the graphical calculus,
    \item substitution in string diagrams using the axioms of braided monoidal categories and the correctness theorem for the graphical calculus on general monoidal categories,
    \item construction of a commuting diagram from the axioms and the coherence theorem for general monoidal categories.
  \end{enumerate}
  \begin{enumerate}[label=(\roman*)]
    \item $\vcenter{\hbox{\includegraphics{proofs_by_hand_1}}}$
    \item $\vcenter{\hbox{\includegraphics{proofs_by_hand_2}}}$
    \item $\vcenter{\hbox{\includegraphics{proofs_by_hand_3}}}$
      ($\sigma_{A, I} = \lambda_{A}^{-1} \of \rho_A$)
  \end{enumerate}
\end{exercise}

@@

@@

@@

@@

>>>>

\usetikzlibrary{fit}
\usetikzlibrary{knots}
\usetikzlibrary{hobby}
\tikzstyle{morphism}=[draw, minimum size=0.5cm, semithick]
\tikzstyle{phantom morphism}=[minimum size=0.5cm]
\tikzstyle{object}=[semithick]
\tikzstyle{cap object}=[object, out=90, in=90, looseness=2]
\tikzstyle{cup object}=[object, out=270, in=270, looseness=2]
\tikzstyle{highlight box}=[draw, dotted]

@@

\begin{answer}
  We construct the morphism as
  \[ \begin{tikzcd}
    (((A \otimes I) \otimes B) \otimes C) \otimes D
      \arrow[d, "((\rho_A \otimes 1_B) \otimes 1_C) \otimes 1_D"] \\
    ((A \otimes B) \otimes C) \otimes D
      \arrow[d, "\alpha_{A, B, C} \otimes 1_D"] \\
    (A \otimes (B \otimes C)) \otimes D
      \arrow[d, "\alpha_{A, B \otimes C, D}"] \\
    A \otimes ((B \otimes C) \otimes D)
      \arrow[d, "1_A \otimes \alpha_{B, C, D}"] \\
    A \otimes (B \otimes (C \otimes D))
      \arrow[d, "1_A \otimes (1_B \otimes (1_C \otimes \lambda_D^{-1}))"] \\
    A \otimes (B \otimes (C \otimes (I \otimes D))).
  \end{tikzcd} \]
  We have no more information about the category except that it is monoidal.
  In this setting we cannot construct two different morphisms of the same type, which follows from the coherence theorem.
\end{answer}

@@

\begin{answer}
  \begin{enumerate}
  \item
    \[ \vcenter{ \hbox{ \begin{tikzpicture}
      \coordinate (in_f) at (0, 0);
      \node[morphism] (f) at (0, 1) {$f$};
      \node[phantom morphism] (f') at (1, 2.5) {};
      \coordinate (out_f) at (1, 3.5);

      \coordinate (in_g) at (1, 0);
      \node[phantom morphism] (g') at (1, 1) {};
      \node[morphism] (g) at (0, 2.5) {$g$};
      \coordinate (out_g) at (0, 3.5);

      \begin{knot}[clip width=8]
        \strand[object] (in_f)
          to node[auto] {$A$} (f.south)
          (f.north) to[out=90, in=270] (f'.south)
          to (f'.north)
          to node[auto] {$A$} (out_f);
        \strand[object] (in_g)
          to node[auto] {$A$} (g'.south)
          to (g'.north)
          to[out=90, in=270] (g.south)
          (g.north) to node[auto] {$A$} (out_g);
      \end{knot}
    \end{tikzpicture}}}
    =
    \vcenter{ \hbox{ \begin{tikzpicture}
      \coordinate (in_f) at (0, 0);
      \node[morphism] (f) at (0, 1) {$g$};
      \node[phantom morphism] (f') at (1, 2.5) {};
      \coordinate (out_f) at (1, 3.5);

      \coordinate (in_g) at (1, 0);
      \node[phantom morphism] (g') at (1, 1) {};
      \node[morphism] (g) at (0, 2.5) {$f$};
      \coordinate (out_g) at (0, 3.5);

      \begin{knot}[clip width=8]
        \strand[object] (in_f)
          to node[auto] {$A$} (f.south)
          (f.north) to[out=90, in=270] (f'.south)
          to (f'.north)
          to node[auto] {$A$} (out_f);
        \strand[object] (in_g)
          to node[auto] {$A$} (g'.south)
          to (g'.north)
          to[out=90, in=270] (g.south)
          (g.north) to node[auto] {$A$} (out_g);
      \end{knot}
    \end{tikzpicture}}} \]

  \item
    \[ \vcenter{ \hbox{ \begin{tikzpicture}
      \coordinate (in) at (0, 0);

      \node[phantom morphism] (g_left) at (-1, 1) {};
      \node[phantom morphism] (g_right) at (1, 1) {};
      \node[morphism, fit=(g_left) (g_right), inner sep=0] (g) {};
      \node at (g) {$g$};

      \node[morphism] (f) at (0, 2) {$f$};

      \node[phantom morphism] (h_left) at (-1, 3) {};
      \node[phantom morphism] (h_right) at (1, 3) {};
      \node[morphism, fit=(h_left) (h_right), inner sep=0] (h) {};
      \node at (h) {$h$};

      \coordinate (out) at (0, 4);

      \draw[object] (in) to node[auto] {$A$} (g);
      \draw[object] (-1, 0 |- g.north) to node[auto] {$B$} (-1, 0 |- h.south);
      \draw[object] (1, 0 |- g.north) to node[auto] {$C$} (1, 0 |- h.south);
      \draw[object] (h) to node[auto] {$D$} (out);
    \end{tikzpicture}}}
    =
    \vcenter{ \hbox{ \begin{tikzpicture}
      \coordinate (in) at (0, 0);

      \node[morphism] (f) at (-1, 1) {$f$};

      \node[phantom morphism] (g_left) at (-1, 2) {};
      \node[phantom morphism] (g_right) at (1, 2) {};
      \node[morphism, fit=(g_left) (g_right), inner sep=0] (g) {};
      \node at (g) {$g$};

      \node[phantom morphism] (h_left) at (-1, 3) {};
      \node[phantom morphism] (h_right) at (1, 3) {};
      \node[morphism, fit=(h_left) (h_right), inner sep=0] (h) {};
      \node at (h) {$h$};

      \coordinate (out) at (0, 4);

      \draw[object] (in) to node[auto] {$A$} (g);
      \draw[object] (-1, 0 |- g.north) to node[auto] {$B$} (-1, 0 |- h.south);
      \draw[object] (1, 0 |- g.north) to node[auto] {$C$} (1, 0 |- h.south);
      \draw[object] (h) to node[auto] {$D$} (out);
    \end{tikzpicture}}} \]

  \item
    \[ \vcenter{ \hbox{ \begin{tikzpicture}
      \coordinate (A_in) at (0, 0);
      \coordinate (C_in) at (1, 0);
      \coordinate (B_in) at (2, 0);
      \node[phantom morphism] (C_1) at (0, 1.5) {};

      \node[phantom morphism] (f_left) at (1, 1.5) {};
      \node[phantom morphism] (f_right) at (2, 1.5) {};
      \node[morphism, fit=(f_left) (f_right), inner sep=0] (f) {};
      \node at (f) {$f$};

      \coordinate (out) at (0, 2);

      \draw[object] (B_in) to node[auto, at start] {$B$} (B_in |- f.south);

      \begin{knot}[clip width=8]
        \strand[object, out=90, in=270] (A_in)
          to node[auto, at start] {$A$} (C_in |- f.south);
        \strand[object, out=90, in=270] (C_in)
          to node[auto, at start] {$C$} (C_1.south)
          to (out);
      \end{knot}
    \end{tikzpicture}}}
    =
    \vcenter{ \hbox{ \begin{tikzpicture}
      \coordinate (A_in) at (0, 0);
      \coordinate (C_in) at (1, 0);
      \coordinate (B_in) at (2, 0);
      \node[phantom morphism] (C_1) at (2, 1.5) {};

      \node[phantom morphism] (f_left) at (0, 1.5) {};
      \node[phantom morphism] (f_right) at (1, 1.5) {};
      \node[morphism, fit=(f_left) (f_right), inner sep=0] (f) {};
      \node at (f) {$f$};

      \coordinate (out) at (2, 2);

      \draw[object] (A_in) to node[auto, at start] {$A$} (A_in |- f.south);

      \begin{knot}[clip width=8]
        \strand[object, out=90, in=270] (C_in)
          to node[auto, at start] {$C$} (C_1.south)
          to (out);
        \strand[object, out=90, in=270] (B_in)
          to node[auto, at start] {$B$} (C_in |- f.south);
      \end{knot}
    \end{tikzpicture}}} \]
  \end{enumerate}

  The correctness theorem for the graphical calculus on symmetric monoidal categories tells us that two diagrams describe the same morphism if and only if they are isotopic in four-dimensional space.
  This means essentially that nodes can move accross edges and that edges can move \textit{through} each other.
  With this we can see that equations (b) and (c) hold, but not equation (a).
\end{answer}

@@

\begin{answer}
  \begin{enumerate}
  \item
    We regard the diagrams up to planar isotopy.
    Thus diagrams (1) and (2) are equal but (3) and (4) are not equal to any other diagram.
  \item
    We regard the diagrams up to spacial isotopy.
    Thus diagrams (1), (2) and (3) are equal but (4) is not equal to any other diagram.
  \item
    We regard the diagrams up to four-dimensional isotopy.
    Thus all diagrams are equal.
  \end{enumerate}
\end{answer}

\ifdefined\issolution \else \pagebreak \fi
\begin{exercise}
  Verify the correctness of the following graphical equations in braided monoidal categories by
  \begin{enumerate}
    \item the correctness theorem of the graphical calculus,
    \item substitution in string diagrams using the axioms of braided monoidal categories and the correctness theorem for the graphical calculus on general monoidal categories,
    \item construction of a commuting diagram from the axioms and the coherence theorem for general monoidal categories.
  \end{enumerate}
  \begin{enumerate}[label=(\roman*)]
    \item $\vcenter{\hbox{\includegraphics{proofs_by_hand_1}}}$
    \item $\vcenter{\hbox{\includegraphics{proofs_by_hand_2}}}$
    \item $\vcenter{\hbox{\includegraphics{proofs_by_hand_3}}}$
      ($\sigma_{A, I} = \lambda_{A}^{-1} \of \rho_A$)
  \end{enumerate}
\end{exercise}

\begin{answer}
  \begin{enumerate}
  \item
    In three-dimensional space, the diagrams are obviously isotopic.
    The equations follow directly from the correctness theorem.
  \item
    \begin{enumerate}
    \item
      \[
        \vcenter{ \hbox{ \begin{tikzpicture}
          \node[phantom morphism] (in) at (0, -0.5) {};
          \node[phantom morphism] (f_left) at (1, 2) {};
          \node[phantom morphism] (f_right) at (2, 2) {};
          \node[morphism, fit=(f_left) (f_right), inner sep=0] (f) {};
          \node[phantom morphism] (out_1) at (0, 4) {};
          \node[phantom morphism] (out_2) at (1, 4) {};
          \node[phantom morphism] (out_3) at (2, 4) {};

          \begin{knot}[clip width=8]
            \strand[object, out=90, in=270] (in)
              to (in |- f.north)
              to (out_2);
            \strand[object, out=90, in=270] (f_left) to (out_1);
            \strand[object, out=90, in=270] (f_right) to (out_3);
          \end{knot}
        \end{tikzpicture} } }
        =
        \vcenter{ \hbox{ \begin{tikzpicture}[use Hobby shortcut]
          \node[phantom morphism] (in) at (2.5, -0.5) {};
          \node[phantom morphism] (f_left) at (0.5, 1) {};
          \node[phantom morphism] (f_right) at (1.5, 1) {};
          \node[morphism, fit=(f_left) (f_right), inner sep=0] (f) {};
          \node[phantom morphism] (out_1) at (1, 4) {};
          \node[phantom morphism] (out_2) at (2, 4) {};
          \node[phantom morphism] (out_3) at (3, 4) {};

          \begin{knot}[clip width=8]
            \strand[object, out=90, in=270] (in)
              to (in |- f.north)
              to (1, 2.5)
              to (out_2);
            \strand[object, in angle=-90, out angle=90, in=-90, out=90] (f_left.north)
              .. (1.6, 1.92)
              .. (out_2 |- 0, 2.5)
              to (out_1);
            \strand[object, in angle=-90, out angle=90, in=-90, out=90]
              (f_right.north)
              .. (1.9, 1.83)
              .. (out_3 |- 0, 2.5)
              to (out_3);
          \end{knot}
        \end{tikzpicture} } }
        =
        \vcenter{ \hbox{ \begin{tikzpicture}
          \node[phantom morphism] (in) at (2, 0) {};
          \node[phantom morphism] (f_left) at (0, 1) {};
          \node[phantom morphism] (f_right) at (1, 1) {};
          \node[morphism, fit=(f_left) (f_right), inner sep=0] (f) {};
          \node[phantom morphism] (out_1) at (0, 4.5) {};
          \node[phantom morphism] (out_2) at (1, 4.5) {};
          \node[phantom morphism] (out_3) at (2, 4.5) {};

          \begin{knot}[clip width=8]
            \strand[object, out=90, in=270] (in)
              to (in |- f.north)
              to (0, 3)
              to (out_2);
            \strand[object, in=-90, out=90] (f_left.north)
              to (0, 2)
              to (1, 3)
              to (out_1);
            \strand[object, in=-90, out=90]
              (f_right.north)
              to (2, 2.5)
              to (out_3);
          \end{knot}
        \end{tikzpicture} } }
        =
        \vcenter{ \hbox{ \begin{tikzpicture}
          \node[phantom morphism] (in) at (2, 0) {};
          \node[phantom morphism] (f_left) at (0, 1) {};
          \node[phantom morphism] (f_right) at (1, 1) {};
          \node[morphism, fit=(f_left) (f_right), inner sep=0] (f) {};
          \node[phantom morphism] (out_1) at (0, 4.5) {};
          \node[phantom morphism] (out_2) at (1, 4.5) {};
          \node[phantom morphism] (out_3) at (2, 4.5) {};

          \begin{knot}[clip width=8]
            \strand[object, out=90, in=270] (in)
              to (in |- f.north)
              to (1, 2.5)
              to (out_2);
            \strand[object, out=90, in=270] (f_left) to (out_1);
            \strand[object, out=90, in=270] (f_right) to (2, 2.5) to (out_3);
          \end{knot}
        \end{tikzpicture} } }
      \]
      In step one we apply naturality of $\sigma^{-1}$, in step two we apply one hexagon equality and in step three we cancel inverses.
      Note that we implicitly use the equality from (iii) to justify that we cross the invisible unit object below the box with another object in step one.

    \item
      \[
        \vcenter{ \hbox{ \begin{tikzpicture}
          \begin{knot}[clip width=8]
            \strand[object, in=-90, out=90]
              (0, 0)
              to (1, 1)
              to (2, 2)
              to (2, 3);
            \strand[object, in=-90, out=90]
              (1, 0)
              to (0, 1)
              to (0, 2)
              to (1, 3);
            \strand[object, in=-90, out=90]
              (2, 0)
              to (2, 1)
              to (1, 2)
              to (0, 3);
          \end{knot}

          % \draw[highlight box] (-0.2, 0) rectangle (2.2, 2);
        \end{tikzpicture} } }
        =
        \vcenter{ \hbox{ \begin{tikzpicture}[use Hobby shortcut]
          \begin{knot}[clip width=8]
            \strand[object, in=-90, out=90]
              (0, 0)
              to (2, 2)
              to (2, 3);
            \strand[object, in angle=-90, out angle=90, in=-90, out=90]
              (1, 0)
              .. (0.9, 1)
              .. (0, 2)
              to (1, 3);
            \strand[object, in angle=-90, out angle=90, in=-90, out=90]
              (2, 0)
              .. (1.1, 1)
              .. (1, 2)
              to (0, 3);
          \end{knot}
        \end{tikzpicture} } }
        =
        \vcenter{ \hbox{ \begin{tikzpicture}[use Hobby shortcut]
          \begin{knot}[clip width=8]
            \strand[object, in=-90, out=90]
              (0, 0)
              to (0, 1)
              to (2, 3);
            \strand[object, in angle=-90, out angle=90, in=-90, out=90]
              (1, 0)
              to (2, 1)
              .. (1.1, 2)
              .. (1, 3);
            \strand[object, in angle=-90, out angle=90, in=-90, out=90]
              (2, 0)
              to (1, 1)
              .. (0.9, 2)
              .. (0, 3);
          \end{knot}

          % \draw[highlight box] (-0.2, 1) rectangle (2.2, 3);
        \end{tikzpicture} } }
        =
        \vcenter{ \hbox{ \begin{tikzpicture}
          \begin{knot}[clip width=8]
            \strand[object, in=-90, out=90]
              (0, 0)
              to (0, 1)
              to (1, 2)
              to (2, 3);
            \strand[object, in=-90, out=90]
              (1, 0)
              to (2, 1)
              to (2, 2)
              to (1, 3);
            \strand[object, in=-90, out=90]
              (2, 0)
              to (1, 1)
              to (0, 2)
              to (0, 3);
          \end{knot}
        \end{tikzpicture} } }
      \]
      We apply one hexagon equality in step one, naturality of $\sigma$ in step two and the other hexagon equality in step three.

    \item
      \[
        \vcenter{ \hbox{ \begin{tikzpicture}[x=0.75cm]
          \begin{knot}[clip width=8]
            \strand[object, in=-90, out=90] (-1, 0) to (1, 4.5);
            \strand[object, dashed, in=-90, out=90] (1, 0) to (-1, 4.5);
          \end{knot}
        \end{tikzpicture} } }
        =
        \vcenter{ \hbox{ \begin{tikzpicture}[x=0.75cm]
          \begin{knot}[clip width=8]
            \strand[object, in=-90, out=90]
              (0, 0)
              to (0, 4.5);
            \strand[object, dashed, in=-90, out=90]
              (1, 0)
              to (-1, 1.5)
              to (1, 3)
              to (-1, 4.5);
          \end{knot}
        \end{tikzpicture} } }
        =
        \vcenter{ \hbox{ \begin{tikzpicture}[x=0.75cm]
          \begin{knot}[clip width=8]
            \strand[object, in=-90, out=90]
              (0, 0)
              to (0, 4.5);
            \strand[object, dashed, in=-90, out=90]
              (1, 0)
              to (-1, 1.4)
              to (-1, 1.6)
              to (1, 3.1)
              (-1, 1.4)
              to (1, 2.9)
              to (1, 3.1)
              to (-1, 4.5);
          \end{knot}
        \end{tikzpicture} } }
        =
        \vcenter{ \hbox{ \begin{tikzpicture}[x=0.75cm]
          \begin{knot}[clip width=8]
            \strand[object, in=-90, out=90]
              (0, 0)
              to (0, 4.5);
            \strand[object, dashed, in=-90, out=90]
              (1, 0)
              to (-1, 1)
              to (-1, 2)
              to (1, 3.5)
              (-1, 1)
              to (1, 2.5)
              to (1, 3.5)
              to (-1, 4.5);
          \end{knot}
        \end{tikzpicture} } }
        =
        \vcenter{ \hbox{ \begin{tikzpicture}[x=0.75cm]
          \begin{knot}[clip width=8]
            \strand[object]
              (0, 0)
              to (0, 4.5);
            \strand[object, dashed, dashed, in=-90, out=90]
              (1, 0)
              to (-1, 1)
              to (1, 2)
              to[in=0] (0, 2.5)
              (0, 2)
              to[out=180] (-1, 2.5)
              to (1, 3.5)
              to (-1, 4.5);
          \end{knot}
        \end{tikzpicture} } }
        =
        \vcenter{ \hbox{ \begin{tikzpicture}[x=0.75cm]
          \begin{knot}[clip width=8]
            \strand[object]
              (0, 0)
              to (0, 4.5);
            \strand[object, dashed, in=-90, out=90]
              (1, 0)
              to[in=-45] (0, 3)
              (0, 1.5)
              to[out=135] (-1, 4.5);
          \end{knot}
        \end{tikzpicture} } }
        =
        \vcenter{ \hbox{ \begin{tikzpicture}[x=0.75cm]
          \begin{knot}[clip width=8]
            \strand[object]
              (0, 0)
              to (0, 4.5);
            \strand[object, dashed, in=-90, out=90]
              (1, 0)
              to[in=-45] (0, 1.5)
              (0, 3)
              to[out=135] (-1, 4.5);
          \end{knot}
        \end{tikzpicture} } }
      \]
      We introduce $\sigma$ with it's inverse in step one.
      We apply naturality of $\sigma^{-1}$ in step two and one hexagon equation in step three.
      The rest follows from the correctness of the graphical calculus for general monoidal categories and cancellation of inverses.
    \end{enumerate}
  \item
    \begin{enumerate}
    \item
      \[ \begin{tikzcd}[column sep=0.5cm]
        & B
          \arrow[ld, "\rho_B^{-1}"']
          \arrow[rd, "\lambda_B^{-1}"] \\
        %
        B \otimes I
          \arrow[rr, "\sigma_{B, I}"]
          \arrow[d, "1_B \otimes f"] &&
        I \otimes B
          \arrow[d, "f \otimes 1_B"] \\
        %
        B \otimes (A \otimes C)
          \arrow[rr, "\sigma_{B, A \otimes C}"]
          \arrow[d, "\alpha_{B, A, C}^{-1}"] &&
        (A \otimes C) \otimes B
          \arrow[d, "\alpha_{A, C, B}"] \\
        %
        (B \otimes A) \otimes C
          \arrow[d, "\sigma_{B, A} \otimes 1_C"] &&
        A \otimes (C \otimes B)
          \arrow[d, "1_A \otimes \sigma_{C, B}"] \\
        %
        (A \otimes B) \otimes C
          \arrow[rr, "\alpha_{A, B, C}"] &&
        A \otimes (B \otimes C)
      \end{tikzcd} \]
      The left outer path describes the first diagram and the right outer path describes the second diagram.
      From top to bottom, the parts commute by the equality from (iii), naturality of $\sigma$ and one hexagon equality.

    \item
      \[ \begin{tikzcd}[column sep=1.2cm]
        (A \otimes B) \otimes C
          \arrow[r, "\alpha_{A, B, C}"]
          \arrow[d, "\sigma_{A, B} \otimes 1_C"] &
        A \otimes (B \otimes C)
          \arrow[d, "1_A \otimes \sigma_{B, C}"] \\
        %
        (B \otimes A) \otimes C
          \arrow[d, "\alpha_{B, A, C}"] &
        A \otimes (C \otimes B)
          \arrow[d, "\alpha_{A, C, B}^{-1}"] \\
        %
        B \otimes (A \otimes C)
          \arrow[r, "\sigma_{B, A \otimes C}"]
          \arrow[d, "1_B \otimes \sigma_{A, C}"] &
        (A \otimes C) \otimes B
          \arrow[d, "\sigma_{A, C} \otimes 1_B"] \\
        %
        B \otimes (C \otimes A)
          \arrow[r, "\sigma_{B, C \otimes A}"]
          \arrow[d, "\alpha_{B, C, A}^{-1}"] &
        (C \otimes A) \otimes B
          \arrow[d, "\alpha_{C, A, B}"] \\
        %
        (B \otimes C) \otimes A
          \arrow[d, "\sigma_{B, C} \otimes 1_A"] &
        C \otimes (A \otimes B)
          \arrow[d, "1_C \otimes \sigma_{A, B}"] \\
        %
        (C \otimes B) \otimes A
          \arrow[r, "\alpha_{C, B, A}"] &
        C \otimes (B \otimes A)
      \end{tikzcd} \]
      The left outer path describes the first diagram and the right outer path describes the second diagram.
      The parts of the diagram commute by the hexagon equalities and naturality of $\sigma$.

    \item
      \[ \begin{tikzcd}
        I \otimes A
          \arrow[rrrrrr, bend left, "\sigma"]
          \arrow[r, "\sigma"]
          \arrow[rrdd, "\rho^{-1}"']
          \arrow[rrrddd, bend right, "\lambda"'] &
        A \otimes I
          \arrow[rrrr, bend left, "\sigma"]
          \arrow[r, "1 \otimes \lambda^{-1}"]
          \arrow[rd, "\rho^{-1}"'] &
        A \otimes (I \otimes I)
          \arrow[rr, "\sigma"]
          \arrow[d, "\alpha^{-1}"] &&
        (I \otimes I) \otimes A
          \arrow[d, "\alpha"'] &
        I \otimes A
          \arrow[l, "\lambda^{-1} \otimes 1"']
          \arrow[ld, "\lambda^{-1}"] &
        A \otimes I
          \arrow[l, "\sigma"']
          \arrow[lldd, "\lambda^{-1}"]
          \arrow[lllddd, bend left, "\rho"] \\
        %
        && (A \otimes I) \otimes I
          \arrow[d, "\sigma \otimes 1"] &&
        I \otimes (I \otimes A)
          \arrow[d, "1 \otimes \sigma"'] \\
        %
        && (I \otimes A) \otimes I
          \arrow[rr, "\alpha"] &&
        I \otimes (A \otimes I) \\
        %
        &&& A
      \end{tikzcd} \]
      The rectangle in the middle represents one hexagon equality.
      The section above it commutes by naturality of $\sigma$.
      The squares to it's right and left commute by naturality of $\lambda$ and $\rho$.
      Everything else commutes trivially or by the coherence theorem for general monoidal categories.
    \end{enumerate}
  \end{enumerate}
\end{answer}

@@

\begin{answer}
  You can define the associator, unitors and symmetry by composition of the corresponding morphisms for products and coproducts as well as distributivity.
  As compositions of natural isomorphisms they will also be natural isomorphisms.
  You can then check the triangle, pentagon and hexagon equalities and show that the symmetry is self-inverse (Application of a proof assistant adviced).

  Another approach is to look at a category that includes $\Set$ as subcategory but makes the monoid structure more obvious.
  We observe that $I$ and $\otimes$ coincide with the terminal object and the product functor from the category of sets with partial functions.
  Liker every terminal object and product, they give rise to a monoidal structure.
  Since the associator, unitors and symmetry are isomorphisms, they are total and contained in $\Set$.
  Thus the monoidal structure exists also $\Set$.
\end{answer}

@@

\begin{answer}
  \[
    \vcenter{ \hbox{ \begin{tikzpicture}
      \node[phantom morphism] (epsilon_left) at (0, 1) {};
      \node[phantom morphism] (epsilon_right) at (1, 1) {};
      \node[morphism, fit=(epsilon_left) (epsilon_right), inner sep=0] (epsilon) {};
      \node at (epsilon) {$\varepsilon$};

      \coordinate (in1) at (0, -0.5);
      \coordinate (in2) at (1, -0.5);
      \draw[object] (in1) to (epsilon_left);
      \draw[object] (in2) to (epsilon_right);
    \end{tikzpicture} } }
    =
    \vcenter{ \hbox{ \begin{tikzpicture}
      \node[phantom morphism] (epsilon_left) at (0, 1) {};
      \node[phantom morphism] (epsilon_right) at (1, 1) {};
      \node[morphism, fit=(epsilon_left) (epsilon_right), inner sep=0] (epsilon) {};
      \node at (epsilon) {$\varepsilon$};

      \node[phantom morphism] (eta_left) at (1, 0) {};
      \node[phantom morphism] (eta_right) at (2, 0) {};
      \node[morphism, fit=(eta_left) (eta_right), inner sep=0] (eta) {};
      \node at (eta) {$\eta$};

      \node[phantom morphism] (epsilon'_left) at (2, 1) {};
      \node[phantom morphism] (epsilon'_right) at (3, 1) {};
      \node[morphism, fit=(epsilon'_left) (epsilon'_right), inner sep=0] (epsilon') {};
      \node at (epsilon') {$\varepsilon'$};

      \coordinate (in1) at (0, -0.5);
      \coordinate (in2) at (3, -0.5);
      \draw[object] (in1) to (epsilon_left);
      \draw[object] (eta_left) to (epsilon_right);
      \draw[object] (eta_right) to (epsilon'_left);
      \draw[object] (in2) to (epsilon'_right);
    \end{tikzpicture} } }
    =
    \vcenter{ \hbox{ \begin{tikzpicture}
      \node[phantom morphism] (epsilon'_left) at (2, 1) {};
      \node[phantom morphism] (epsilon'_right) at (3, 1) {};
      \node[morphism, fit=(epsilon'_left) (epsilon'_right), inner sep=0] (epsilon') {};
      \node at (epsilon') {$\varepsilon'$};

      \coordinate (in1) at (2, -0.5);
      \coordinate (in2) at (3, -0.5);
      \draw[object] (in1) to (epsilon'_left);
      \draw[object] (in2) to (epsilon'_right);
    \end{tikzpicture} } }
  \]
  In the first step we apply the snake equation for $\varepsilon$ and in the second step the snake equation for $\varepsilon'$.
\end{answer}

@@

\begin{answer}
  We only show the equivalence $L \otimes 0 \iso 0$.
  The other equivalences are analogous.

  We define functions in both directions by
  \[ \begin{tikzpicture}
    \node[phantom morphism] (f_left) at (1, 1) {};
    \node[phantom morphism] (f_right) at (2, 1) {};
    \node[morphism, fit=(f_left) (f_right), inner sep=0] (f) {};
    \node at (f) {$!$};

    \node[phantom morphism] (L_mid) at (0, 1) {};

    \coordinate (in_L) at (0, 0);
    \coordinate (in_0) at (1.5, 0);
    \coordinate (out) at (2, 2);

    \draw[object] (in_L)
      to node[auto] {$L$} (L_mid.south)
      to (L_mid.north)
      to[cap object] (f_left);
    \path (f_left) to node[auto, swap] {$R$} (f_left |- out);
    \draw[object] (in_0) to node[auto] {$0$} (f);
    \draw[object] (f_right) to node[auto, swap] {$0$} (out);
  \end{tikzpicture} \]
  and
  \[ \begin{tikzpicture}
    \node[phantom morphism] (f_left) at (0, 0) {};
    \node[phantom morphism] (f_right) at (1, 0) {};
    \node[morphism, fit=(f_left) (f_right), inner sep=0] (f) {};
    \node at (f) {$!$};

    \draw[object] (0.5, -1) to node[auto] {$0$} (f);
    \draw[object] (f_left) to node[auto] {$L$}  (0, 1);
    \draw[object] (f_right) to node[auto] {$0$}  (1, 1);
  \end{tikzpicture}. \]
  In one direction they are trivially inverse because morphisms to $0$ are unique.
  In the other direction it follows by
  \[
    \vcenter{ \hbox{ \begin{tikzpicture}
      \node[phantom morphism] (f_left) at (1, 1) {};
      \node[phantom morphism] (f_right) at (2, 1) {};
      \node[morphism, fit=(f_left) (f_right), inner sep=0] (f) {};
      \node at (f) {$!$};

      \node[phantom morphism] (g_left) at (1.5, 2) {};
      \node[phantom morphism] (g_right) at (2.5, 2) {};
      \node[morphism, fit=(g_left) (g_right), inner sep=0] (g) {};
      \node at (g) {$!$};

      \node[phantom morphism] (L_mid) at (0, 1) {};

      \coordinate (in_L) at (0, 0);
      \coordinate (in_0) at (1.5, 0);
      \coordinate (out_L) at (1.5, 3);
      \coordinate (out_0) at (2.5, 3);

      \draw[object] (in_L)
        to node[auto] {$L$} (L_mid.south)
        to (L_mid.north)
        to[cap object] (f_left);
      \path (f_left) to node[auto, swap] {$R$} (f_left |- g.south);
      \draw[object] (in_0) to node[auto] {$0$} (f);
      \draw[object] (f_right) to node[auto, swap] {$0$} (g);
      \draw[object] (g_left) to node[auto] {$L$} (out_L);
      \draw[object] (g_right) to node[auto] {$0$} (out_0);
    \end{tikzpicture} } }
    =
    \vcenter{ \hbox{ \begin{tikzpicture}
      \node[phantom morphism] (f_left) at (1, 1) {};
      \node[phantom morphism] (f_right) at (2.5, 1) {};
      \node[morphism, fit=(f_left) (f_right), inner sep=0] (f) {};
      \node at (f) {$!$};

      \node[phantom morphism] (g_left) at (2, 2) {};
      \node[phantom morphism] (g_right) at (3, 2) {};
      \node[morphism, fit=(g_left) (g_right), inner sep=0] (g) {};
      \node at (g) {$!$};

      \node[phantom morphism] (L_mid_1) at (0, 1) {};
      \node[phantom morphism] (L_mid_2) at (0, 2) {};
      \node[phantom morphism] (R_mid) at (1, 2) {};

      \coordinate (in_L) at (0, 0);
      \coordinate (in_0) at (1.75, 0);
      \coordinate (out_L) at (2, 3);
      \coordinate (out_0) at (3, 3);

      \draw[object] (in_L)
        to node[auto] {$L$} (L_mid_1.south)
        to (L_mid_2.north)
        to[cap object] (R_mid)
        to (f_left);
      \path (R_mid) to node[auto, swap] {$R$} (R_mid |- out_L);
      \draw[object] (in_0) to node[auto] {$0$} (f);
      \draw[object] (f_right) to node[auto] {$0$} (g);
      \draw[object] (g_left) to node[auto, swap] {$L$} (out_L);
      \draw[object] (g_right) to node[auto, swap] {$0$} (out_0);

      \node[highlight box, fit=(f) (g)] {};
    \end{tikzpicture} } }
    =
    \vcenter{ \hbox{ \begin{tikzpicture}
      \node[phantom morphism] (f_left) at (1, 1) {};
      \node[phantom morphism] (f_right) at (2.5, 1) {};
      \node[phantom morphism, fit=(f_left) (f_right), inner sep=0] (f) {};

      \node[phantom morphism] (g_left) at (2, 2) {};
      \node[phantom morphism] (g_right) at (3, 2) {};
      \node[phantom morphism, fit=(g_left) (g_right), inner sep=0] (g) {};

      \node[phantom morphism] (L_mid_1) at (0, 1) {};
      \node[phantom morphism] (L_mid_2) at (0, 2) {};
      \node[phantom morphism] (R_mid) at (1, 2) {};
      \node[phantom morphism] (L_mid_3) at (2, 2) {};

      \coordinate (in_L) at (0, 0);
      \coordinate (in_0) at (3, 0);
      \coordinate (out_L) at (2, 3);
      \coordinate (out_0) at (3, 3);

      \draw[object] (in_L)
        to node[auto] {$L$} (L_mid_1.south)
        to (L_mid_2.south)
        to (L_mid_2.north)
        to[cap object] (R_mid)
        to (R_mid.south)
        to[cup object] (L_mid_3)
        to (L_mid_3.north)
        to node[auto, swap] {$L$} (out_L);
      \path (R_mid) to node[auto, swap] {$R$} (R_mid |- out_L);
      \draw[object] (in_0)
        to node[auto] {$0$} (in_0 |- f.south)
        to (out_0 |- g.south)
        to (out_0 |- g.north)
        to node[auto, swap] {$0$} (out_0);

      \node[highlight box, fit=(f_left) (g_right)] {};
    \end{tikzpicture} } }
    =
    \vcenter{ \hbox{ \begin{tikzpicture}
      \node[phantom morphism] (L_mid) at (0, 1) {};
      \node[phantom morphism] (0_mid) at (1, 1) {};

      \draw[object] (0, 0)
        to node[auto] {$L$} (L_mid.south)
        to (0, 3);
      \draw[object] (1, 0)
        to node[auto] {$0$} (0_mid.south)
        to (1, 3);
    \end{tikzpicture} } }.
  \]
  In the second step we use again that morphisms to $0$ are unique.
\end{answer}

@@

\begin{answer}
  For clarity, we draw $\eta$ as
  \[ \begin{tikzpicture}
    \draw[object] (0, 0.5)
      to node[auto, swap] {$R$} (0, 0)
      to[cup object] (1, 0)
      to node[auto] {$L$} (1, 0.5);
    \end{tikzpicture} \]
    and $\varepsilon$ as
    \[ \begin{tikzpicture}
      \draw[object] (0, -0.5)
        to node[auto] {$L$} (0, 0)
        to[cap object] (1, 0)
        to node[auto, swap] {$R$} (1, -0.5);
    \end{tikzpicture}. \]
